### 2015-04-20 paper.tex
Remove author summary
Fix labels and remove template text
Remove template table and fix labels

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta
erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante
cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend
volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar
non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim
ultrices, ultrices elit pulvinar, volutpat risus.

@@

Dimensional analysis provides scaling laws that are used to upscale model test
data into performance and design information for a full-scale prototype turbine.
For hydrokinetic turbines, hydrodynamic similitude is achieved when the Reynolds
number, Froude number and tip-speed-ratio of the model and the full scale device
match. The Reynolds number is defined as
\begin{equation}
Re_L = \frac{UL}{\nu},
\label{eq-Re}
\end{equation}
where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
kinematic viscosity. The Froude number is defined as
\begin{equation}
Fr = \frac{U}{\sqrt{gL}},
\label{eq-Fr}
\end{equation}
where $g$ is the gravitational acceleration, and the tip speed ratio is defined
as
\begin{equation}
\lambda=\frac{\omega R}{U_\infty},
\end{equation}
where $\omega$ and $R$ are the rotor angular velocity and radius.
For hydrokinetic turbine testing, $Re$, not $Fr$, is the dominant scaling
parameter. However, the Froude number (based on blade tip submergence) should
remain small (significantly below one). It is rare to achieve perfect similitude
for $Re$, but a threshold value should be exceeded, such that scale model
results can be extrapolated.

@@

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} 
Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec 
pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cp-curves}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cd-curves}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Power Coefficient Reynolds Number Dependence.}
Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{cp-re-dep}
\end{figure}

@@

% Please do not create a heading level below \subsection. For 3rd level
% headings, use \paragraph{}.
\subsection*{Subsection 1}
Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel
massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit
amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo
eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla
erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim
semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\subsection*{Subsection 2}
\paragraph{3rd Level Heading.} Nulla mi mi, venenatis sed ipsum varius, volutpat
euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et
dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue
semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel
sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque.
Praesent faucibus semper libero.

>>>>

@@

Dimensional analysis provides scaling laws that are used to upscale model test
data into performance and design information for a full-scale prototype turbine.
For hydrokinetic turbines, hydrodynamic similitude is achieved when the Reynolds
number, Froude number and tip-speed-ratio of the model and the full scale device
match. The Reynolds number is defined as
\begin{equation}
Re_L = \frac{UL}{\nu},
\label{eq:Re}
\end{equation}
where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
kinematic viscosity. The Froude number is defined as
\begin{equation}
Fr = \frac{U}{\sqrt{gL}},
\label{eq:Fr}
\end{equation}
where $g$ is the gravitational acceleration, and the tip speed ratio is defined
as
\begin{equation}
\lambda=\frac{\omega R}{U_\infty},
\end{equation}
where $\omega$ and $R$ are the rotor angular velocity and radius.
For hydrokinetic turbine testing, $Re$, not $Fr$, is the dominant scaling
parameter. However, the Froude number (based on blade tip submergence) should
remain small (significantly below one). It is rare to achieve perfect similitude
for $Re$, but a threshold value should be exceeded, such that scale model
results can be extrapolated.

@@

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cp-curves}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cd-curves}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Power Coefficient Reynolds Number Dependence.}
Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{fig:cp-re-dep}
\end{figure}

@@

\subsection*{Strut drag losses}
